Solent region: Test Maps

### 2021-07-30 Solent_Mapping_v2.Rmd
Changed the fuel poverty comparision to 2012 and 2018 and mapped the fuel poverty change of the cities in more detail

```{r Loading in the 2019 Local Authority Fuel Poverty Data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LA_Fuel_Poverty.csv")
la_fuelpov_2019<-readr::read_csv(inFile)
head(la_fuelpov_2019)
```
```{r Mapping Local Authority Fuel Poverty 2021}
la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Codes` # Creating a variable with the local authority code in the same name 
la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
la_merged_Fuelpov2019$pcFP <- as.numeric(la_merged_Fuelpov2019$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
ggplot2::ggplot(la_merged_Fuelpov2019) +
  geom_sf(aes(fill = pcFP)) +
  scale_fill_gradient(name = "Proportion of households fuel poor (%)", low="green",high="red")
```

### Actual Difference between 2012-2019
```{r Loading in the difference data}
#Green indicates a smaller increase in fuel poverty from 2012 to 2019
#Red indicates an increase in fuel poverty from 2012 to 2019
```

@@

```{r Mapping the LSOA 2021 Fuel Poverty}
lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
  geom_sf(aes(fill=pcFP))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```

# The end

```{r environment}
R.Version()

>>>>

```{r Loading in the 2019 Local Authority Fuel Poverty Data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LA_Fuel_Poverty.csv")
la_fuelpov_2019<-readr::read_csv(inFile)
head(la_fuelpov_2019)
```
```{r Mapping Local Authority Fuel Poverty 2019}
la_fuelpov_2019$lad18cd <- la_fuelpov_2019$`Area Codes` # Creating a variable with the local authority code in the same name 
la_merged_Fuelpov2019 <- merge(la_sf_data, la_fuelpov_2019)# Merge the local Authority boundaries and the Fuel Poverty data
la_merged_Fuelpov2019$pcFP <- as.numeric(la_merged_Fuelpov2019$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
ggplot2::ggplot(la_merged_Fuelpov2019) +
  geom_sf(aes(fill = pcFP)) +
  scale_fill_gradient(name = "Proportion of households fuel poor (%)", low="green",high="red")
```

### Difference in proportion Fuel Poverty 2012 to 2019
```{r Creating the idfference in proportion variable}
#Green indicates a smaller increase in fuel poverty from 2012 to 2019
#Red indicates an increase in fuel poverty from 2012 to 2019
fp_LA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LA_Fuel_Poverty.csv"))
fp_LA_2019_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2019 LA_Fuel_Poverty.csv"))
merged_df <- merge(fp_LA_2012_df, fp_LA_2019_df, by = "Area Code", all = TRUE)
names(merged_df)
merged_df$pc_diff <-  as.numeric(merged_df$`Proportion of households fuel poor (%)`) - merged_df$`Proportion of households fuel poor (%) 2012`
```
```{r Mapping the iddference in fuel poverty from 2012 to 2019}
merged_df$lad18cd <- la_fuelpov_2019$`Area Code` # Creating a variable with the local authority code in the same name 
la_merged_Fuelpov20192012dif <- merge(la_sf_data,merged_df)# Merge the local Authority boundaries and the Fuel Poverty data
la_merged_Fuelpov20192012dif$pcFP <- as.numeric(la_merged_Fuelpov20192012dif$`Proportion of households fuel poor (%)`) # convert to numeric from char - why does it load as char??
ggplot2::ggplot(la_merged_Fuelpov20192012dif) +
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green",high="red")
```

@@

```{r Mapping the LSOA 2019 Fuel Poverty}
lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
  geom_sf(aes(fill=pcFP))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
####Mapping the difference in proportion of fuel poverty from 2012 to 2018

```{r Creating the dfference in proportion variable}
#Green indicates a smaller increase in fuel poverty from 2012 to 2018
#Had to use 2018 as the metric for fuel poverty has changed in 2019 
#Red indicates an increase in fuel poverty from 2012 to 2018
fp_LSOA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2012_df$pc2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
fp_LSOA_2018_df$pc2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
names(merged_df)
merged_df$pc_diff <-  as.numeric(merged_df$pc2018) - merged_df$pc2012
summary(merged_df)
```
```{r Mapping the change in Fuel Poverty}
merged_df$LSOA11CD <- merged_df$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov20122018 <- merge(lsoa_sf_data, merged_df) #merging these
ggplot2::ggplot(lsoa_fuelpov20122018) +
  geom_sf(aes(fill=pc_diff))+ 
  scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
##### Looking at cities in more detail
```{r Looking at Southampton in more detail}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Southampton")

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Southampton")
#Around Bargate and Freemantle increased fuel poverty
```
```{r Looking at Portsmouth in more detail}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Portsmouth")

# plotting the change in fuel poverty from 2018-2012 of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
#Charles Dickens increased fuel poverty
```
```{r Looking at Winchester in more detail}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Winchester")

# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
